---
title: "abhardw3_Assignment5"
author: "Aarush Bhardwaj"
date: "09/11/2021"
output: pdf_document
---

```{r}
# Setting Working Directory

 setwd("D:/A_Sem_2/Quantative Management Modeling/Assignments/Assignment 5/Quant_Assignment5")
```

# Installing the required packages.

```{r}
library(Benchmarking)
library(tidyverse)
```

COMPUTING FORMULATION

```{r}
# creating the vectors

input  <-  matrix(c(150,400,320,520,350,  320,  200,  700,  1200,  2000,  1200,  700),ncol  =  2) 
output <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000, 15000),ncol = 2)

# Assigning names to columns

colnames(output) <- c("staff_daily_hours","supplies_daily")
colnames(input) <- c("daily_reimbursed_patient", "daily_privately_paid_patient")

# values of input & output

input
output
```

It is clear from the table above that the results are similar to the performance data table from the Hope Valley Health Care Association's 6 nursing facilities.

Now, we will use a tool called "DEA" that can help organizations to identify and allocate their resources to enhance their efficiency.

# DEA Analysis (Using FDH)
```{r}
analysis_fdh<-  dea(input,output,RTS  =  "fdh")

eff_fdh <- as.data.frame(analysis_fdh$eff)

colnames(eff_fdh)  <-  c("efficiency_fdh")

peer_fdh  <-  peers(analysis_fdh)

colnames(peer_fdh) <- c("peer1_fdh")

lambda_fdh <- lambda(analysis_fdh)

colnames(lambda_fdh) <- c("L1_fdh", "L2_fdh", "L3_fdh", "L4_fdh", "L5_fdh", "L6_fdh")

peer_lamb_eff_fdh  <-  cbind(peer_fdh,  lambda_fdh,  eff_fdh)

peer_lamb_eff_fdh
```

```{r}
# Plotting results
dea.plot(input,output,RTS="fdh", main="Free disposability hull (FDH) Graph")

```


# DEA Analysis (Using CRS)
```{r}
analysis_crs <- dea(input,output,RTS = "crs")

eff_crs <- as.data.frame(analysis_crs$eff)

colnames(eff_crs) <- c("efficiency_crs")

peer_crs <- peers(analysis_crs)

colnames(peer_crs) <- c("peer1_crs", "peer2_crs", "peer3_crs")

lambda_crs <- lambda(analysis_crs)

colnames(lambda_crs) <- c("L1_crs", "L2_crs", "L3_crs", "L4_crs")

peer_lamb_eff_crs <- cbind(peer_crs, lambda_crs, eff_crs)

peer_lamb_eff_crs
```

```{r}
# Plotting results
dea.plot(input,output,RTS="crs", main="Constant Returns to Scale (CRS) Graph")
```

# DEA Analysis (Using VRS)
```{r}
analysis_vrs  <-  dea(input,output,RTS  =  "vrs")

eff_vrs <- as.data.frame(analysis_vrs$eff)

colnames(eff_vrs)  <-  c("efficiency_vrs")

peer_vrs <- peers(analysis_vrs)

colnames(peer_vrs) <- c("peer1_vrs", "peer2_vrs", "peer3_vrs")

lambda_vrs <- lambda(analysis_vrs)

colnames(lambda_vrs) <- c("L1_vrs", "L2_vrs", "L3_vrs", "L4_vrs", "L5_vrs")

peer_lamb_eff_vrs <- cbind(peer_vrs, lambda_vrs, eff_vrs)

peer_lamb_eff_vrs

```

```{r}
# Plotting results
dea.plot(input,output,RTS="vrs", main="Variable Returns to Scale (VRS) Graph")
```

# DEA Analysis (Using IRS)
```{r}
analysis_irs  <-  dea(input,output,RTS  =  "irs")

eff_irs <- as.data.frame(analysis_irs$eff)

colnames(eff_irs)  <-  c("efficiency_irs")

peer_irs <- peers(analysis_irs)

colnames(peer_irs)  <-  c("peer1_irs",  "peer2_irs",  "peer3_irs")

lambda_irs  <-  lambda(analysis_irs)

colnames(lambda_irs) <- c("L1_irs", "L2_irs", "L3_irs", "L4_irs", "L5_irs")

peer_lamb_eff_irs <- cbind(peer_irs, lambda_irs, eff_irs)

peer_lamb_eff_irs
```

```{r}
# Plotting results
dea.plot(input,output,RTS="irs",  main="Increasing  Returns  to  Scale  (IRS) Graph")
```

# DEA Analysis (Using DRS)
```{r}
analysis_drs  <-  dea(input,output,RTS  =  "drs")

eff_drs <- as.data.frame(analysis_drs$eff)

colnames(eff_drs)  <-  c("efficiency_drs")

peer_drs <- peers(analysis_drs)

colnames(peer_drs) <- c("peer1_drs", "peer2_drs", "peer3_drs")

lambda_drs <- lambda(analysis_drs)

colnames(lambda_drs) <- c("L1_drs", "L2_drs", "L3_drs", "L4_drs")

peer_lamb_eff_drs <- cbind(peer_drs, lambda_drs, eff_drs)

peer_lamb_eff_drs
```

```{r}
# Plotting results
dea.plot(input,output,RTS="drs", main="Decreasing Returns to Scale (DRS) Graph")
```

# DEA Analysis (Using FRH)
```{r}
analysis_frh  <-  dea(input,output,RTS  =  "add")

eff_frh <- as.data.frame(analysis_frh$eff)

colnames(eff_frh) <- c("efficiency_frh")

peer_frh <- peers(analysis_frh)

colnames(peer_frh) <- c("peer1_frh")

lambda_frh <- lambda(analysis_frh)

colnames(lambda_frh) <- c("L1_frh", "L2_frh", "L3_frh", "L4_frh", "L5_frh", "L6_frh")

peer_lamb_eff_frh <- cbind(peer_frh, lambda_frh, eff_frh)

peer_lamb_eff_frh
```

```{r}
# Plotting results
dea.plot(input,output,RTS="add", main="Free Replicability Hull (FRH) Graph")
```


# Comparing among different assumptions
```{r}
dea.plot(input,output,RTS="fdh", main="Free disposability hull (FDH) Graph")

dea.plot(input,output,RTS="vrs", main="Variable Returns to Scale (VRS) Graph")

dea.plot(input,output,RTS="drs", main="Decreasing Returns to Scale (DRS) Graph")

dea.plot(input,output,RTS="irs",  main="Increasing  Returns  to  Scale  (IRS)  Graph")

dea.plot(input,output,RTS="crs", main="Constant Returns to Scale (CRS) Graph")

dea.plot(input,output,RTS="add", main="Free Replicability Hull (FRH) Graph")
```

The above charts allows us to compare the results of each DEA model.

Let's talk a little about each one of them.
FDH is the smallest technology set, as shown and it seeks to create fewer outputs (number of patient days reimbursed by third-party sources and number of patient days reimbursed privately) with more inputs (number of patient days reimbursed by third-party sources and number of patient days reimbursed privately) (staffing labor and the cost of supplies). 

FDH is the most popular model among businesses, yet it has several flaws owing to its assumptions. As we can see, all of the efficiency of this model are only 1, however it is not as efficient as we thought when compared to other models since we identify areas/units to improve.

VRS is larger than FDH because it “fills-out” the spaces that FDH reduced. Here we can see that unit 6 can improve its efficiency.

As the graphs show, DRS and IRS are bigger than VRS. For smaller input values, DRS seeks to enlarge the set, whereas the IRS tries to raise the technology. Units 5 and 6 might increase their efficiency, according to DRS, and facility 6 could improve as well, according to IRS.

CRS is the largest technology set, allowing us to assess whether there are any conceivable scaling up or down combinations. Units 5 and 6 require improvement based on the efficiency numbers.

The purpose of FRH, which is larger than FDH but less than CRS, is to replace deterministic data with random variables.


## Question 2 - Research and Development Division of Emax Corporation

Objective function:

max: 20 X1 + 15 X2 + 25 X3 - 6 Y1P - 6 Y1M - 3 Y2M
S.T :
Employment Level

6x1 + 4x2 + 5x3 - (Y1P - Y1M)  = 50

Earnings Next Year
 
8x1 + 7x2 + 5x3 - (Y2P - Y2M)  = 75
 
Non-negativity constraint
 

X1, X2, X3 >= 0
Y1P, Y1M, Y2P, Y2M >= 0
```{r}
library(lpSolveAPI)

# Load the data
emax <-  read.lp("E_Max.lp")
emax
```

```{r}
solve(emax)
```

The solver returns 0 as an output. This means that it is able to find a solution.

```{r}
get.objective(emax)
```

Here we are maximizing the profit by reducing other goals of the company. The value 225 is the penalty for failing to meet the goals on the objective function.
```{r}
get.variables(emax)
```

The above order results from order of the variables in the objective function.

So for us, the results are:

X1 = 0,X2 = 0,X3 = 15,Y1P = 25,Y1M = 0,Y2M = 0,Y2P = 0

This means that the earning (Y2) expectations are fully satisfied.

For workforce, the goal projected exceeds by 25 and based on the total profit of product 3, it has a negative result on its profit by 15.
```{r}

```